---
title: "Cross Validaton"
output: github_document
---

```{r}

library(tidyverse)
library(modelr)
library(mgcv)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)

```

## Simulate data

```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )
```

Look at the data

```{r}
nonlin_df %>% 
  ggplot(aes(x=x, y=y))+
  geom_point()
```

## Cross validation--by hand

Get training and testing datasets
```{r}
train_df= sample_n(nonlin_df, size=80)

test_df=anti_join(nonlin_df, train_df, by="id")
```

Fit three models

```{r}
linear_mod=lm(y~x, data=train_df)
smooth_mod=gam(y~ s(x), data=train_df)
wiggly_mod=gam (y~ s(x, k=30), sp=10e-6, data=train_df)
```

can i see what i just did..

```{r}
train_df %>% 
  add_predictions(linear_mod) %>% 
  ggplot(aes(x=x, y=y))+
  geom_point ()+
  geom_line(aes(y=pred), color="red")

train_df %>% 
  add_predictions(smooth_mod) %>% 
  ggplot(aes(x=x, y=y))+
  geom_point ()+
  geom_line(aes(y=pred), color="red")

train_df %>% 
  add_predictions(wiggly_mod) %>% 
  ggplot(aes(x=x, y=y))+
  geom_point ()+
  geom_line(aes(y=pred), color="red")
  
```

Gather models

```{r}
train_df %>% 
  gather_predictions(wiggly_mod, smooth_mod, wiggly_mod) %>% 
  ggplot(aes(x=x, y=y))+
  geom_point ()+
  geom_line(aes(y=pred), color="red")+
  facet_grid(. ~ model)
  
```

Look at prediction accuracy

```{r}
rmse(linear_mod, test_df)
rmse(wiggly_mod, test_df)
rmse(smooth_mod, test_df)
```

## Cross validation using `modelr`

```{r}

cv_df=
  crossv_mc(nonlin_df, 100)
```

What is happening here...

```{r}
cv_df %>% pull(train) %>% .[[1]] %>% as_tibble()
cv_df %>% pull(test) %>% .[[1]] %>% as_tibble()
```
```{r}
cv_df=
  cv_df %>% 
  mutate(
    train=map(train, as_tibble),
    test= map(test, as_tibble)
  )
```

Let's try to fit models and get RMSEs for them

```{r}
cv_df=
cv_df %>% 
  mutate(
    linear_mod=map(.x=train, ~lm(y~x, data=.x)),
    smooth_mod=map(.x=train, ~gam(y~s(x), data=.x)),
    wiggly_mod= map(.x=train, ~gam(y~s(x,k=30), sp=10e-6,data=.x))
  ) %>% 
  mutate(
    rmse_linear= map2_dbl(.x=linear_mod, .y=test, ~rmse(model= .x, data=.y)),
    rmse_smooth= map2_dbl(.x=smooth_mod, .y=test, ~rmse(model= .x, data=.y)),
    rmse_wiggly= map2_dbl(.x=wiggly_mod, .y=test, ~rmse(model= .x, data=.y))
  )
```
What do these results say about the model

Compute averages..

```{r}

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to="model",
    values_to="rsme",
    names_prefix="rsme_"
  ) %>% 
  group_by(model) %>% 
  summarize(avg_rmse=mean(rmse))
```
##Try on a real dataset

import my data

```{r}

child_growth_df = 
  read_csv("./data/nepalese_children.csv") %>% 
  mutate(
    weight_cp=(weight>7)*(weight-7)
  )

```

weight vs arm circumference

```{r}
child_growth_df %>% 
  ggplot(aes(x=weight, y=armc))+
  geom_point(alpha=.3)
```

Fit the models

```{r}
linear_mod= lm(armc~weight, data=child_growth_df)
pwlin_mod= lm(armc~weight+weight_cp, data=child_growth_df)
smooth_mod= gam(armc~ s(weight), data=child_growth_df)
```

```{r}
child_growth_df %>% 
  gather_predictions(linear_mod, pwlin_mod, smooth_mod) %>% 
  ggplot(aes(x=weight, y=armc))+
  geom_point(alpha=.3) +
  geom_line(aes(y=pred), color="red")+
  facet_grid(.~model)
               
```

Try to understand model fit using CV.

```{r}
cv_df=
  crossv_mc(child_growth_df, 100) %>% 
  mutate(
    train=map(train, as_tibble),
    test= map(test, as_tibble)
  )
```

```{r}
cv_df = 
  cv_df %>% 
  mutate(
    linear_mod  = map(train, ~lm(armc ~ weight, data = .x)),
    pwl_mod     = map(train, ~lm(armc ~ weight + weight_cp, data = .x)),
    smooth_mod  = map(train, ~gam(armc ~ s(weight), data = as_tibble(.x)))) %>% 
  mutate(
    rmse_linear = map2_dbl(linear_mod, test, ~rmse(model = .x, data = .y)),
    rmse_pwl    = map2_dbl(pwl_mod, test, ~rmse(model = .x, data = .y)),
    rmse_smooth = map2_dbl(smooth_mod, test, ~rmse(model = .x, data = .y)))
```

Plot the distribution Error

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

